Results Text

### 2024-03-12 Fish Data Analysis/Results_Text.qmd
Small type fix

                            # ### Used to remove every third point to reduce autocorrelation
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
                           group_by(Comp_ID) %>%
                           filter(row_number() %% 3 == 1) %>%
                           ungroup()
```

@@

                           # ### Used to remove every third point to reduce autocorrelation
                           mutate(Date = paste(Year,Month,Day,sep="_"),
                                  Date_Trial = paste(Year,Month,Day,Trial,sep="_")) %>%
                           group_by(Date_Trial) %>%
                           filter(row_number() %% 3 == 1) %>%
                           ungroup()

@@

far_min_dist <- 3
far_max_dist <- 10

>>>>

                           # ### Used to remove every third point to reduce autocorrelation
                           mutate(Date = paste(Year,Month,Day,sep="_"),
                                  Date_Trial = paste(Year,Month,Day,Trial,sep="_")) %>%
                           group_by(Date_Trial) %>%
                           filter(row_number() %% 3 == 1) %>%
                           ungroup()
```

@@

                            # ### Used to remove every third point to reduce autocorrelation
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
                           group_by(Comp_ID) %>%
                           filter(row_number() %% 3 == 1) %>%
                           ungroup()

@@

far_min_dist <- 3
far_max_dist <- 100
